MLH1 data report 

### 2017-10-12 rmd_report.rmd
learning how to permute samples

Currently this section is under construction.
```{r}
# use q_cut_off table, to find the mice to use
listOmice <- q_cutoff_table$mouse[ (q_cutoff_table$total >= 25) ]
#mke new df with from 
df.pasd.mice <- MLH1_data[MLH1_data$mouse %in% listOmice, ]

#write function --- for taking 100 samples of 10

permut.df <- function(df){
  #semperate by mouse
    mouse.data    <- ddply(df, c("mouse"), summarise,
       df <- data.frame(
              samp = sample(nMLH1.foci,5)
            ) 
        )

>>>>

Currently this section is under construction.
```{r}

colnms = c("mouse", "rep")

#makes dfs, with the samples 
permut.mouse.numb <- function(x, rep_size, samp_size){
  new.df = matrix(nrow=rep_size, ncol=samp_size)
for(i in 1:rep_size) {
  new.df[i,] = sample(x, samp_size)
  }
return(as.data.frame(new.df, colnames(colnms) ) )
}

ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]

#make this the function that I apply over the mice in the data
t.test(sample(ply_data$nMLH1.foci, 5), sample(ply_data$nMLH1.foci, 5))$p.value
t.test(sample(ply_data$nMLH1.foci, 13), sample(ply_data$nMLH1.foci, 13))$p.value

#this works
vv <-permut.mouse.numb(df.pasd.mice$nMLH1.foci,5,2)

##
## I think this does it! this makes a list of 23 dfs (for each mouse in the large df)
kk<-dlply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,5) )

jj<-ddply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,10) )

#t.test and p values
#maybe I should just choose 2 samples, do a t.test, do that 100 times..?
#below runs t.tests on 
bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2 samples of size 10

#figure out a way to plot/visualize these pvalues
#2 samples are good for t.tests, but I need to repeat 100 times
#I think I need to ... add the replicates that can be xxply through

## for 1:100, cal permt(10,2) then call 
ll=c()
ty <- for(i in 1:10){
  print(i)
  jj <-ddply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,10) )

  bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )
  #the t.test$p.values are not exactly what they should be
#put p values into a list? (100 pvalues )
  ll[i] = bb$V1[i]#this returns a list of p values for different mice? one mouse?
}

#for

gg<-t.test(kk$`10mar15_PWD_m2`[1,2:5], kk$`10mar15_PWD_m2`$V3)  
#jj$`10mar15_PWD_m2`
#jj[1,1:5]
#$`10mar15_PWD_m2`
#[1] 0.6071011

##then do t.test to test the distributions 
## data is the data frames, by mouse, function is t.test

# use q_cut_off table, to find the mice to use
listOmice <- q_cutoff_table$mouse[ (q_cutoff_table$total >= 25) ]
#mke new df with from 
df.pasd.mice <- MLH1_data[MLH1_data$mouse %in% listOmice, ]

#write function --- for taking 100 samples of 10
permut.df <- function(df){
  #semperate by mouse
    mouse.data    <- ddply(df, c("mouse"), summarise,
       df <- data.frame(
              samp = sample(nMLH1.foci,5)
            ) 
        )
